\documentclass[aps,twocolumn,nobalancelastpage]{revtex4}

\input{preamble}

\begin{document}

\title{Exercise 1: Matrices and Linear Algebra}
\author{Drew Silcock}
\affiliation{Physics Department, University of Bristol}
\date{\today}

\maketitle

\input{sections/introduction}
\input{sections/relaxation}
\input{sections/laplace}
\input{sections/capacitor}
\input{sections/diffusion}

\begin{thebibliography}{99}

    \bibitem{edwards2004}
        Ron Edwards, Bruce H. Falvo and David C. Larson,
        \emph{Elementary Linear Algebra} (5th ed.),
        Chapter 10: Numerical Methods,
        Page 578.
        Houghton Mifflin Company,
        2004.

    \bibitem{golub1996}
        Gene H. Golub and Charles F. Van Loan,
        \emph{Matrix Computations} (3rd ed.).
        Johns Hopkins University Press,
        1996.

    \bibitem{demmel1997}
        James W. Demmel,
        \emph{Applied Numerical Linear Algebra},
        Chapter 6: Iterative Methods for Linear Systems,
        Page 290.
        Society for Pure and Applied Mathematics,
        1997.

    \bibitem{roache1972}
        Patrick J. Roache,
        \emph{Computational Fluid Dynamics} (1st ed.).
        Hermosa,
        1972.

    \bibitem{tannehill1997}
        John C. Tannehill, Dale A. Anderson and Richard H. Pletcher,
        \emph{Computational Fluid Mechanics and Heat Transfer} (2nd ed.).
        Taylor \& Francis,
        1997.

    \bibitem{laney1998}
        Culbert B. Laney,
        \emph{Computational Gasdynamics},
        Chapter 11: Conservation and Other Basic Principles,
        Page 198.
        Cambridge University Press,
        1998.

    \bibitem{hoffman2001}
        Joe D. Hoffman and Steven Frankel,
        \emph{Numerical Methods for Engineers and Scientists} (2nd ed.),
        Chapter 10: Parabolic Partial Differential Equations,
        Page 616.
        CRC Press,
        2001.

    \bibitem{gardner2013}
        Carl Gardner,
        \emph{Numerical Methods for Partial Differential Equations}: course notes,
        Poisson's and Laplace's Equations.
        Arizona State University,
        2013.

\end{thebibliography}

\end{document}